---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sppois

<!-- badges: start -->
[![Build Status](https://travis-ci.com/gregmacfarlane/sppois.svg?branch=master)](https://travis-ci.com/gregmacfarlane/sppois)
[![R-CMD-check](https://github.com/gregmacfarlane/sppois/workflows/R-CMD-check/badge.svg)](https://github.com/gregmacfarlane/sppois/actions)
<!-- badges: end -->

The goal of sppois is to implement the two stage estimator for spatial autoregressive Poisson models proposed by [Lambert et al. (2010)](http://dx.doi.org/10.1016/j.regsciurbeco.2010.04.001)

> This package does not currently implement the Lambert methods. Contributions welcome.

## Installation

sppois is not on CRAN. When it is, you can install the released version of sppois from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sppois")
```

For now, you can install the development version from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gregmacfarlane/sppois")
```
## Example

The package allows users to estimate a full-information maximum likelihood 
estimation of spatially-autogressive poisson count models.

```{r example}
library(sppois)
crime_pois   <- sarpoisson(crime_i ~ income + home_value, data = columbus_crime,
                           listw = columbus_neighbors, method = "non-spatial") 
crime_sppois <- sarpoisson(crime_i ~ income + home_value, data = columbus_crime,
                           listw = columbus_neighbors, method = "fiml") 
summary(crime_sppois)
```

